% ======================================================================
% SUMMARY SECTION
% ======================================================================

\ifdefstring{\summarymode}{none}{}{
    \vspace{0.3 cm}

    \begin{onecolentry}
}
    \ifdefstring{\summarymode}{academic}{
        \begin{itemize}
            \setlength\itemsep{0em}
            \setlength\parskip{0pt}
            \setlength\parsep{0pt}
            \item Ph.D. in \textbf{Artificial Intelligence} from \textbf{DTU Compute}, specializing in \textbf{Embedded AI and TinyML}.
            \item Strong track record of \textbf{peer-reviewed publications} in international IEEE and Elsevier venues.
            \item \textbf{Collaborated with industry partners} (Grundfos, VELUX, Bang \& Olufsen) and secured multiple grants.
            \item \textbf{Supervised and mentored} multiple M.Sc.\ and B.Sc.\ theses and university project courses.
            \item Skilled at bridging complex theoretical research with practical, real-world applications.
        \end{itemize}
    }{}
    
    \ifdefstring{\summarymode}{industry-tinyml}{
        \begin{itemize}
            \setlength\itemsep{0em}
            \setlength\parskip{0pt}
            \setlength\parsep{0pt}
            \item Machine Learning researcher with strong expertise in \textbf{Embedded AI, TinyML, and efficient edge deployment}.
            \item Skilled in developing \textbf{efficient AI pipelines} and applying \textbf{TinyML} techniques for on-device intelligence.
            \item Experienced in supervision, collaboration, and leading technical projects, with a track record of impactful work.
            \item Successful \textbf{collaborations with leading industry partners}, including Grundfos, VELUX, and Bang \& Olufsen.
            \item Passionate about \textbf{advancing AI at the edge} for predictive maintenance, IoT, and intelligent automation.
        \end{itemize}
    }{}
    
    \ifdefstring{\summarymode}{industry-ml}{
        \begin{itemize}
            \setlength\itemsep{0em}
            \setlength\parskip{0pt}
            \setlength\parsep{0pt}
            \item Machine Learning researcher with strong expertise in \textbf{deep learning, model optimization, and automation}.
            \item Specialized in designing, training, and deploying ML models for real-world applications.
            \item Skilled in developing \textbf{efficient AI pipelines} and applying \textbf{TinyML} techniques for on-device intelligence.
            \item Experienced in supervision, collaboration, and leading technical projects, with a track record of impactful work and publications.
        \end{itemize}
    }{}
\ifdefstring{\summarymode}{none}{}{
    \end{onecolentry}
}
