% ======================================================================
% TEACHING EXPERIENCE SECTION
% ======================================================================

\section{Teaching Experience}



    \ifdefstring{\teachingmode}{supercompact}{
        \begin{onecolentry}
            \begin{highlightsforbulletentries}
                \item \textbf{Supervised}: 1 M.Sc. Thesis, 1 B.Sc. Thesis, 3 Project Courses
                \item \textbf{Teaching Assistant}: 7 Semesters. Deep Learning, MLOps, Operating Systems, etc.
            \end{highlightsforbulletentries}
        \end{onecolentry}
    }{}


    \ifdefstring{\teachingmode}{compact}{
        \begin{onecolentry}
            \textbf{Master Thesis Supervision}\\
            Neural Architecture Generation for Edge AI (DTU, 2025, Student: William Diedrichsen Marstrand)

            \vspace{0.2 cm}

            \textbf{Bachelor Thesis Supervision}\\
            Memory Efficient Neural Network Execution (DTU, 2026, Student: Tülin Cetinkaya)

            \vspace{0.2 cm}

            \textbf{Project Course Supervision}\\
            Neural Network Architecture for Resource Constrained Hardware (DTU, 2024), TinyML - Efficient Machine Learning for Embedded AI Systems (DTU, 2024), Embedded Programming for Benchmarking Embedded AI Models (DTU, 2024)

            \vspace{0.2 cm}

            \textbf{Teaching Assistant}\\
            Deep Learning (Sharif, 2021; DTU, 2023), MLOps (DTU, 2025), Operating Systems (DTU, 2023/2024), Parallel Programming and Architectures (Sharif, 2021), Medical Image Analysis and Processing (Sharif, 2021)
        \end{onecolentry}
    }{}    


    \ifdefstring{\teachingmode}{expanded}{
        \multicolentry{*, 3.3cm}
        {
            Master Thesis Supervision: Neural Architecture Generation for Edge AI\\
            Student: William Diedrichsen Marstrand - DTU Compute
        }
        {\raggedleft Jan 2025 - Jun 2025}
        
        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Bachelor Thesis Supervision: Efficient NN Inference with On-the-Fly Decompression\\
            Student: Tülin Cetinkaya - DTU Compute
        }
        {\raggedleft Feb 2026 - Jun 2026}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Project Course Supervision: Neural Network Architecture for Resource Constrained Hardware\\
            Student: William Diedrichsen Marstrand - DTU Compute
        }
        {\raggedleft Oct 2024 - Dec 2024}
        
        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Project Course Supervision: TinyML - Efficient Machine Learning for Embedded AI Systems\\
            Student: William Diedrichsen Marstrand - DTU Compute
        }
        {\raggedleft Jun 2024}
        
        \vspace{0.2 cm}
        
        \multicolentry{*, 3.3cm}
        {
            Project Course Supervision: Embedded Programming for Benchmarking Embedded AI Models\\
            Student: Simon Kristoffer Janum - DTU Compute
        }
        {\raggedleft Feb 2024 - May 2024}
        
        \vspace{0.2 cm}
        
        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: Deep Learning\\
            Instructor: Dr. Jes Frellsen - DTU Compute
        }
        {\raggedleft Sep 2023 - Nov 2023}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: Deep Learning\\
            Instructor: Dr. Emad Fatemizadeh - Sharif University of Technology
        }
        {\raggedleft Sep 2021 - Jan 2022}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: MLOps\\
            Instructor: Dr. Nicki Skafte Detlefsen - DTU Compute
        }
        {\raggedleft Jan 2025}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: Operating Systems\\
            Instructor: Dr. Xenofon Fafoutis - DTU Compute
        }
        {\raggedleft Sep-Nov 2023, 2024}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: Parallel Programming and Architectures\\
            Instructor: Dr. Matin Hashemi - Sharif University of Technology
        }
        {\raggedleft Jan 2021 - Jul 2021}

        \vspace{0.2 cm}

        \multicolentry{*, 3.3cm}
        {
            Teaching Assistant: Medical Image Analysis and Processing\\
            Instructor: Dr. Emad Fatemizadeh - Sharif University of Technology
        }
        {\raggedleft Jan 2021 - Jul 2021}
    }{}
